Research Proposal

### 2012-05-24 dissertation-proposal/research-proposal.tex
Final lit review and proposal

Multimethods play a significant role in Clojure, and a satisfactory
type system for Clojure should understand them to some degree.
There is some experience statically typing multimethods
\cite{Millstein02modularstatically}
, but this is a challenge and may not be addressed in the
timeframe proposed, beyond initial consideration of how it would
fit with the rest of the system.

@@

\begin{description}
\item[0.1]
	\begin{itemize}
	\item Concrete types (no type variables)
	\item Union types
	\item Fixed arity function types
	\item Typed deftype (class definitions)
	\item Uniform variable-arity function types
	\item Type checking without occurance typing
	\item Enough functions annotated from clojure.core for proof-of-concept
	\end{itemize}
\item[0.2]
	\begin{itemize}
	\item Typed defrecord (record structures)
	\item Type variables (polymorphic types)
	\item Most functions annotated from clojure.core library
	\end{itemize}
\item[Challenges]
	\begin{itemize}
	\item Devise strategy for type inference (eg. occurence typing)
	\item Manage interactions between typed namespaces
	\item Mutable reference types
	\item Non-uniform variable arity polymorphism
	\item Typing Multimethods
	\end{itemize}

>>>>

Multimethods play a significant role in Clojure, and a satisfactory
type system for Clojure should understand them to some degree.
There is some experience statically typing multimethods
\cite{Millstein02modularstatically}, 
but this is a challenge and may not be addressed in the
timeframe proposed, beyond initial consideration of how it would
fit with the rest of the system.

@@

\begin{description}
\item[0.1]
	\begin{itemize}
	\item Union types
  \item Basic Local Type Inference algorithm
	\item Fixed arity function types
	\item Typed deftype (class definitions)
	\item Uniform variable-arity function types
	\item Enough functions annotated from clojure.core for proof-of-concept
	\item Bounded Type variables
	\end{itemize}
\item[Challenges]
	\begin{itemize}
	\item Devise strategy for type inference (eg. occurence typing)
	\item Manage interactions between typed namespaces
	\item Mutable reference types
	\item Non-uniform variable arity polymorphism
	\item Typing Multimethods
	\item Fine Grained Hash-Map Types
	\end{itemize}
